A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-08 index.rmd
add bibliography

--- 
knit: "bookdown::render_book"
title: "A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author: "Pratik R. Gupte and others"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::pdf_book
documentclass: book
# bibliography: [refs.bib]
biblio-style: apalike
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Source code for a guide to pre-processing high-frequency tracking data."
---

>>>>

--- 
knit: "bookdown::render_book"
title: "A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author: "Pratik R. Gupte and others"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::pdf_book
documentclass: book
bibliography: [references.bib]
biblio-style: apalike
link-citations: yes
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Source code for a guide to pre-processing high-frequency tracking data."
---
